Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

The computation of $\J^\catt_{i,j}$ is an instance of H-V $k$-SJ. Specifically, collect the top-edges of all rectangles $r_i \in R_i$ into a set $H$, and collect the left-edges of all rectangles $r_j \in R_j$ into a set $V$. This yields an H-V $k$-SJ problem whose input comprises all the $R_z$ with $z \in [k] \setminus \set{i,j}$,  $H$, and $V$. Its output includes every $r_z \in R_z$, for $z \in [k] \setminus \set{i,j}$, $h \in H$, and $v \in V$ such that $h \cap v \cap \bigcap_{z \in [k] \setminus \set{i,j}} r_z \ne \emptyset$.

>>>>

The computation of $\J^\catt_{i,j}$ is an instance of H-V $k$-SJ. Specifically, collect the top-edges of all rectangles $r_i \in R_i$ into a set $H$, and collect the left-edges of all rectangles $r_j \in R_j$ into a set $V$. This yields an H-V $k$-SJ problem whose input comprises all the $R_z$ with $z \in [k] \setminus \set{i,j}$,  $H$, and $V$. Its output includes every $r_z \in R_z$, for $z \in [k] \setminus \set{i,j}$, $h \in H$, and $v \in V$ such that $h \cap v \cap \bigcap_{z \in [k] \setminus \set{i,j}} r_z \ne \emptyset$. There is one-one correspondence between the output of the H-V $k$-SJ and $\J^\catt_{i,j}$. Thus, by Lemma~\ref{lmm:hv}, the H-V $k$-SJ can be solved in $O(k) \cdot (F_{k-1}(n, |\J^\catt_{i,j}|) + n \log n + k \cdot |\J^\catt_{i,j}|)$ time. Converting the output into $\J^\catt_{i,j}$ takes another $O(|\J^\catt_{i,j}|)$ time. Applying the trivial bound $|\J^\catt_{i,j}| \le \out$, we can assert that $\J^\catt_{i,j}$ can be produced in $O(k) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$ time

Performing the above for all $i, j \in [k]$ with $i \ne j$ results in a total time complexity of $O(k^3) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$. A category-1 result tuple $\bm{t}$ may be seen more than once (this happens if the top-left corner of $B_\bm{t}$ is the top-left corner of more than one rectangle in $\bm{t}$). Duplicate removal can be achieved at no extra cost asymptotically, following the ideas explained in Section~\ref{sec:hv:type2}.
